---
title: "Regression Models Course Project"
author: "Mahesh"
date: "12 September 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

Motor Trend, a magazine about the automobile industry, is interested in 
exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). The questions of interest are:  

1. “Is an automatic or manual transmission better for MPG”
2. "Quantify the MPG difference between automatic and manual transmissions" 

### DataSet

mtcars

```{r}
library(ggplot2)
data(mtcars)


```

Inspect the data  

```{r}
head(mtcars)
str(mtcars)

boxplot(mpg ~ am, data = mtcars, xlab="Transmission (0 = Automatic, 1 = Manual)", ylab="MPG",main="Boxplot of MPG vs. Transmission")

pairs(mtcars, panel=panel.smooth, main="Pair Graph of all variables")
```

Convert the variables of interest into factors for analysis  

```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

mean of manual and auto mpg  

```{r}
# Automatic mpg mean
round(mean(mtcars[mtcars$am==0, "mpg"]),2)

# Manual mpg mean
round(mean(mtcars[mtcars$am==1, "mpg"]),2)
```

## Regression Model
t test   

```{r}
t.test(mpg ~ am, data = mtcars)
```

p-value is 0.001374 and we can reject null hypothesis. mean difference is 7


```{r}
par(mfrow=c(2,2))
fullmodel <- lm(mpg ~ ., data=mtcars)
summary(fullmodel)
plot(fullmodel)
```

The above model explains 78% variance of mpg variable 
Residual standard error: 2.833 on 15 degrees of freedom, we need to find 
alternate model  

```{r}
par(mfrow=c(2,2))
altmodel <- step(lm(mpg ~ ., data=mtcars),k =3)
summary(altmodel)
plot(altmodel)
```

The above model explains 84% variance of mpg variable 

```{r}
par(mfrow=c(2,2))
altmodel2 <- lm(mpg ~ wt*am + qsec, data=mtcars)
summary(altmodel2)
plot(altmodel2)
```

The above model explains 88% variance of mpg variable 

```{r}
par(mfrow=c(2,2))
altmodel3 <- lm(mpg ~ am, data=mtcars)
summary(altmodel3)
plot(altmodel3)
```

The above model explains 34% variance of mpg variable  

Now we try to select the final model

```{r}
anova(altmodel3,altmodel,fullmodel,altmodel2)
summary(altmodel2)$coef
```

From the above "mpg ~ qsec + wt*am"" has the  highest adjusted R-Squared values  

above model suggest that cars with manual transmission add more mileage on 
decreasing weight with the equation 14.08 -2.94*wt.

```{r}
max(cooks.distance(altmodel2))
par(mfrow=c(1,1))
plot(cooks.distance(altmodel2))
```








